Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-17 finalReportPres.tex
A few comments on final presentation and the report. More to come

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}
\usepackage{amsmath,amssymb,amsfonts,bm}

@@

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{Large}
    		Model autonomous vehicle subsystems for a Lexus platform
    \end{Large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{Large}
    		Use neural network modeling techniques to develop plant models
    \end{Large}
  \end{block}
\end{frame}

@@

\begin{frame}{System Architecture}{}
	\begin{block}{System Architecture}
    \begin{large}
      The overall system architecture of this project consists of six subsystems: 
      \begin{itemize}
          \item Steering
          \item Acceleration
          \item Brake %Model
          \item Shift %Model
          \item Speed %Model
          \item Speed control %Model
        \end{itemize} 
    \end{large}
  \end{block}
\end{frame}

@@

\begin{frame}{Modeling using Neural Networks}{}
	\begin{block}{}
		\begin{figure}
			\centering
      \tikzset{%
        input neuron/.style={
          circle,
          fill=green!50,
          minimum size=0.7cm
        },
        neuron missing/.style={
          draw=none, 
          scale=1,
          fill=white,
          text height=0.01cm,
          execute at begin node=\color{black}$\vdots$
        },
      }

@@

      \begin{tikzpicture}[x=1.5cm, y=1.5cm]

@@

        \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
        \draw[->,ultra thick](3,-2.5) -- (3,1.6);

      \end{tikzpicture}
  \caption{Actor neural network structure for approximating control input.}
  \label{fig:nnActor}
		\end{figure}
	\end{block}
\end{frame}

\begin{frame}
Therefore, approximated actor signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W}_a = 
  \begin{bmatrix}
    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  \end{bmatrix}.
\end{align*}
%

Now take $\eta$ data points and form the set of linear equations as: %
%
\begin{align*}
&  \bm{\sigma}^T(\mathbf{e}_k) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k}^{[d]}\right)^T\\
 & \bm{\sigma}^T(\mathbf{e}_{k+1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+1}^{[d]}\right)^T\\
                                            &\vdots \\
 & \bm{\sigma}^T(\mathbf{e}_{k+\eta-1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+\eta-1}^{[d]}\right)^T  
\end{align*}
%

@@

Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
%
\begin{align*}
  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
\end{align*}
%
Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
%
\begin{align}
  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
  \label{eq:actorWeightsGradient}
\end{align}
%
Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
\begin{align*}
  {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
\end{align*}

@@

\begin{frame}
$\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:

@@

@@

@@

>>>>

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
% \usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}
\usepackage{amsmath,amssymb,amsfonts,bm}

@@

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    Given input-output data of different subsystems, such as steering, acceleration, brake, shift, speed, and speed control, of an autonomous (self-driving) vehicle:
    \begin{itemize}
    \item Develop mathematical and/or block diagram models of these subsystems

    \item Develop machine learning-based models for the major subsystems of Lexus self-driving vehicle
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{itemize}
    \item Use state-space modeling techniques based on input and output data

    \item Use system identification modeling techniques

    \item Use machine learning (neural network) based modeling techniques
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}{System Architecture}{}
  \missingfigure{Place the overall vehicle picture from the report that shows different subsystems  }
	\begin{block}{System Architecture}
    The overall system architecture of this project consists of six subsystems: 
    \begin{itemize}
        \item Steering
        \item Acceleration
        \item Brake %Model
        \item Shift %Model
        \item Speed %Model
        \item Speed control %Model
      \end{itemize} 
  \end{block}
\end{frame}

@@

\begin{frame}{Modeling using Neural Networks}{}
  \begin{figure}
    \centering
    \tikzset{%
      input neuron/.style={
        circle,
        fill=green!50,
        minimum size=0.7cm
      },
      neuron missing/.style={
        draw=none, 
        scale=1,
        fill=white,
        text height=0.01cm,
        execute at begin node=\color{black}$\vdots$
      },
    }

@@

    \begin{tikzpicture}[x=1.5cm, y=1.3cm,transform shape]

@@

      \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
      \draw[->,ultra thick](3,-2.5) to[bend left] (3,1.6);

    \end{tikzpicture}
    \caption{Actor neural network structure for approximating control input.}
    \label{fig:nnActor}
		\end{figure}
\end{frame}

\begin{frame}

\todo[inline]{Use generic input and output symbols instead of my own symbols that I used to inputs (error) and outputs (control inputs) }
  Therefore, approximated actor signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W}_a = 
  \begin{bmatrix}
    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  \end{bmatrix}.
\end{align*}
%

Now take $\eta$ data points and form the set of linear equations as: %
%
\begin{align*}
&  \bm{\sigma}^T(\mathbf{e}_k) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k}^{[d]}\right)^T\\
 & \bm{\sigma}^T(\mathbf{e}_{k+1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+1}^{[d]}\right)^T\\
                                            &\vdots \\
 & \bm{\sigma}^T(\mathbf{e}_{k+\eta-1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+\eta-1}^{[d]}\right)^T  
\end{align*}
%
\end{frame}

@@

Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
%
\begin{align*}
  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
\end{align*}
%
Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
%
\begin{align}
  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
  \label{eq:actorWeightsGradient}
\end{align}
%

@@

\begin{frame}

  Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
  \begin{align*}
    {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
  \end{align*}

$\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:

@@

\todo[inline]{In your case, there is no actor neural network, I implemented generic reinforcement learning structures using actor critic neural network structure}

@@

\begin{frame}

  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
\end{frame}

@@

\begin{frame}{Validation and Testing}{Model Validation}
	\begin{figure}
		\centering \includegraphics[width=.45\linewidth]{figs/img/aStuffValidationBrakeModel}\quad%
		\caption{Model Validation Setup}
    			\label{fig:validationSetup}
		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item Testing data points using Control Desk software  \end{itemize} \end{minipage}\\[1em]
	\end{figure}
\end{frame}
